---
title: "Covid-19 CZ Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: lumen
    runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(zoo)
library(rmarkdown)
library(knitr)
library(ggpubr)
library(shiny)
library(deSolve)
library(plotly)

k.roll <- 7
l.roll <- 30


url.testy <- "https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/testy.csv"
url.nakaza <- "https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/nakaza.csv"
url.minus <- "https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/nakazeni-vyleceni-umrti-testy.csv"
url.zaklad <- "https://onemocneni-aktualne.mzcr.cz/api/v2/covid-19/zakladni-prehled.csv"

testy <- read.csv(url.testy)
nakaza <- read.csv(url.nakaza)
minus <- read_csv(url.minus)
zaklad.stat <- read.csv(url.zaklad)

jk <- ifelse(nrow(nakaza) == nrow(testy),procenta <-  nakaza$prirustkovy_pocet_nakazenych/testy$prirustkovy_pocet_testu, procenta <- nakaza$prirustkovy_pocet_nakazenych[1:(nrow(nakaza)-1)]/testy$prirustkovy_pocet_testu)

prehledT.procenta <- round(procenta,4)*100

prehledT <- data.frame(tail(testy$datum, 5),tail(testy$prirustkovy_pocet_testu, 5),tail(testy$kumulativni_pocet_testu, 5),tail(prehledT.procenta, 5))
colnames(prehledT) <- c("Date","Daily tests","Cumulative number of tests","Test positivity (in %)")

prehledN <- data.frame(tail(nakaza$datum, 5), tail(nakaza$prirustkovy_pocet_nakazenych, 5), tail(nakaza$kumulativni_pocet_nakazenych, 5), tail(minus$kumulativni_pocet_vylecenych, 5), tail(minus$kumulativni_pocet_umrti, 5))
colnames(prehledN) <- c("Date","Daily cases","Cumulative number of cases","Cumulative number of recovered", "Cumulative number of deaths")


sir_1 <- function(beta, gamma, theta, S0, I0, R0, D0, times) {
  require(deSolve) # for the "ode" function
  
  # the differential equations:
  sir_equations <- function(time, variables, parameters) {
    with(as.list(c(variables, parameters)), {
      dS <- -beta * I * S
      dI <-  beta * I * S - gamma * I - theta * I
      dR <-  gamma * I
      dD <-  theta * I
      return(list(c(dS, dI, dR, dD)))
    })
  }
  # the parameters values:
  parameters_values <- c(beta  = beta, gamma = gamma, theta = theta)
  
  # the initial values of variables:
  initial_values <- c(S = S0, I = I0, R = R0, D = D0)
  
  # solving
  out <- ode(initial_values, times, sir_equations, parameters_values)
  
  # returning the output:
  as.data.frame(out)
}

beta <- 0.0000000148 #infect ratio
gamma <- 0.088 #recovery 
theta <- 0.0009 #umrtnost
lambda <- 0.0364 #hospitalizovan??
S0 <- 10000000
I0 <- 5752
R0 <- 18933
D0 <- 428

times <- seq(0, 250)
kapacita <- 15500
datumy <- seq.Date(as.Date("2020-09-01"), by = 1, along.with = times)

rho <- S0*beta/gamma

data <- sir_1(beta = beta, gamma = gamma, theta = theta, S0 = S0, I0 = I0, R0 = R0, D0 = D0, times)
H <- data$I*lambda
data <- data_frame(data,H, datumy)

p.1 <- ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_line(aes(y = I, color = "Infected")) +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_line(aes(y = S, color = "Susceptible")) +
  geom_line(aes(y = R, color = "Recovered")) +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(color = "Legend")


p.2 <- ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_line(aes(y = I, color = "Infected")) +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_line(aes(y = R, color = "Recovered")) +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(color = "Legend")


p.3 <- ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_line(aes(y = I, color = "Infected")) +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(color = "Legend")


p.4 <- ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(color = "Legend")



nakaza <- read.csv(url.nakaza, stringsAsFactors = FALSE)

minus$new <- minus$kumulativni_pocet_nakazenych - minus$kumulativni_pocet_vylecenych - minus$kumulativni_pocet_umrti

data <- sir_1(beta = beta, gamma = gamma, theta = theta, S0 = S0, I0 = I0, R0 = R0, D0 = D0, times)
H <- data$I*lambda

minusV <- minus$new[nakaza$datum >= "2020-09-01"]
datumZ <- nakaza$datum[nakaza$datum >= "2020-09-01"]
minusD <- minus$kumulativni_pocet_umrti[nakaza$datum >= "2020-09-01"]
datazariV <- data_frame(as.factor(datumZ), minusV,minusD)
data <- data_frame(data,H, datumy)



Roll.Mean.Dates <- testy$datum[(1+(k.roll-1)/2):(nrow(testy)-(k.roll-1)/2)] 
Roll.Mean.Values <- rollmean(testy$prirustkovy_pocet_testu,k.roll) 
testy.roll <- data.frame(Roll.Mean.Dates,Roll.Mean.Values) 
title.plot <- paste(k.roll, " day rollmean") 


Roll.Mean.Dates.last.l <- tail(Roll.Mean.Dates, l.roll)
Roll.Mean.Values.last.l <- tail(Roll.Mean.Values, l.roll)
testy.roll.Last.l <- data_frame(Roll.Mean.Dates.last.l, Roll.Mean.Values.last.l)
title.plot.l <- paste("Last ",l.roll, " days") 


Roll.Mean.Dates.nakaza <- nakaza$datum[(1+(k.roll-1)/2):(nrow(nakaza)-(k.roll-1)/2)] 
Roll.Mean.Values.nakaza <- rollmean(nakaza$prirustkovy_pocet_nakazenych,k.roll) 
nakaza.roll <- data.frame(Roll.Mean.Dates.nakaza,Roll.Mean.Values.nakaza) 
nakaza.title.plot <- paste(k.roll, " day rollmean") 


Roll.Mean.Dates.last.l.nakaza <- tail(Roll.Mean.Dates.nakaza, l.roll)
Roll.Mean.Values.last.l.nakaza <- tail(Roll.Mean.Values.nakaza, l.roll)
nakaza.roll.Last.l <- data_frame(Roll.Mean.Dates.last.l.nakaza, Roll.Mean.Values.last.l.nakaza)
nakaza.title.plot.l <- paste("Last ",l.roll, " days") 


jk <- ifelse(nrow(nakaza) == nrow(testy),procenta <-  nakaza$prirustkovy_pocet_nakazenych/testy$prirustkovy_pocet_testu, procenta <- nakaza$prirustkovy_pocet_nakazenych[1:(nrow(nakaza)-1)]/testy$prirustkovy_pocet_testu)

datum <- testy$datum

df.procenta <- data_frame(datum,procenta)

Roll.Mean.Dates.procenta <- df.procenta$datum[(1+(k.roll-1)/2):(nrow(df.procenta)-(k.roll-1)/2)] 
Roll.Mean.Values.procenta <- rollmean(df.procenta$procenta,k.roll) 
procenta.roll <- data.frame(Roll.Mean.Dates.procenta,Roll.Mean.Values.procenta) 
procenta.title.plot <- paste(k.roll, " day rollmean") 


Roll.Mean.Dates.last.l.procenta <- tail(Roll.Mean.Dates.procenta, l.roll)
Roll.Mean.Values.last.l.procenta <- tail(Roll.Mean.Values.procenta, l.roll)
procenta.roll.Last.l <- data_frame(Roll.Mean.Dates.last.l.procenta, Roll.Mean.Values.last.l.procenta)
procenta.title.plot.l <- paste("Last ",l.roll, " days")


Dates.last.l.procenta <- tail(df.procenta$datum, l.roll)
Values.last.l.procenta <- tail(df.procenta$procenta, l.roll)
Last.l <- data_frame(Dates.last.l.procenta, Values.last.l.procenta)


celkova.pozitiva.testu <- nakaza$kumulativni_pocet_nakazenych[nrow(nakaza)]/testy$kumulativni_pocet_testu[nrow(testy)]
celkova.pozitiva.testu30 <- (nakaza$kumulativni_pocet_nakazenych[nrow(nakaza)]-nakaza$kumulativni_pocet_nakazenych[nrow(nakaza)-30])/(testy$kumulativni_pocet_testu[nrow(testy)]-testy$kumulativni_pocet_testu[nrow(testy)-30])

cpt <- round(celkova.pozitiva.testu*100,3)
cpt30 <- round(celkova.pozitiva.testu30*100,3)

last.date <- nakaza$datum[nrow(nakaza)]

```

Overview
=====================

Column 
-----------------------------------------------------------------------

### Chart A

```{r}
valueBox(formatC(zaklad.stat$aktivni_pripady, big.mark = " "), caption = "Active cases", icon = "ion-android-alert")
```

### Chart A

```{r}
valueBox(formatC(zaklad.stat$aktualne_hospitalizovani, big.mark = " "), caption = "Currently hospitalized", icon = "ion-alert-circled")
```

### Chart A

```{r}
valueBox(paste(round(zaklad.stat$aktualne_hospitalizovani/zaklad.stat$aktivni_pripady,4)*100,"%"), caption = "Proportion of infected needing hospital", icon = "ion-alert-circled")
```

### Chart A

```{r}
valueBox(paste(round(tail(minus$kumulativni_pocet_umrti,1)/tail(nakaza$kumulativni_pocet_nakazenych,1), 4)*100,"%"), caption = "Mortality", icon = "ion-alert-circled")
```


Column 
-----------------------------------------------------------------------

### Tests

```{r}

kable(prehledT,caption = "Basic overview (Tests)")

```

Column 
-----------------------------------------------------------------------

### Decease

```{r}
kable(prehledN,caption = "Basic overview (Decease)")
```

Column 
-----------------------------------------------------------------------

### Information

Last update: ``r Sys.time()``.

Newest data are from ``r last.date`` from the website of the Ministry of Health of Czech Republic (https://onemocneni-aktualne.mzcr.cz/covid-19)



SIR Models
=====================

Column
----------------------

```{r}

info1 <- paste("Peak will happen on ",data$datumy[data$I == max(data$I)], "with number of confirmed cases equal to ",round(data$I[data$I == max(data$I)])
      , "and ",round(data$H[data$I == max(data$I)][1]),"people at the hospital at the time.")

info2 <- paste("Capacity of hospital, which is equal to ",kapacita,"beds, will be overreached on ",data$datumy[data$H > kapacita][1])

info3 <- paste("Sum of all Covid-19 cases will be ", round(max(data$R)))

info4 <- paste("Number of deaths will be",round(max(data$D)))

info5 <- paste("Rho is equal to ",round(rho,3))

```

### Chart A

```{r}
valueBox(data$datumy[data$I == max(data$I)], caption = "Peak date", icon = "ion-android-alert")
```

### Chart A

```{r}
valueBox(prettyNum(round(data$I[data$I == max(data$I)]), big.mark = " "), caption = "Peak active cases", icon = "ion-android-alert")
```

### Chart A

```{r}
valueBox(prettyNum(round(data$H[data$I == max(data$I)][1]), big.mark = " "), caption = "Needing hospital at peak", icon = "ion-android-alert")
```

### Chart A

```{r}

valueBox(data$datumy[data$H > kapacita][1], caption = "Hospitals ovecrowded", icon = "ion-android-alert")

```




Column {.tabset .tabset-fade}
----------------------

### Deceased/Infected/Hospitalized/Susceptible/Recovered

```{r}
ggplotly(p.1)
```

### Deceased/Infected/Hospitalized/Recovered

```{r}

ggplotly(p.2)

```

### Deceased/Infected/Hospitalized

```{r}

ggplotly(p.3)

```

### Deceased/Hospitalized

```{r}

ggplotly(p.4)

```

Column
----------------------


### Chart A

```{r}

valueBox(prettyNum(round(max(data$R)), big.mark = " "), caption = "Total infected till the end", icon = "ion-android-person")

```

### Chart A

```{r}

valueBox(prettyNum(round(max(data$D)), big.mark = " "), caption = "Number of deaths", icon = "ion-android-person")

```

### Chart A

```{r}
valueBox(round(rho,3), caption = "Rho value", icon = "ion-android-warning")
```


Column {.tabset}
----------------------

### Deceased/Hospitalized/Infected

```{r}

ggplotly(ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_line(aes(y = I, color = "Infected")) +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_point(shape = 20, data = datazariV, aes(x = as.Date(datumZ), y = minusV), color = "blue2") +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(title = "Model comparison to real data",color = "Legend"))

```

### Deceased

```{r}

ggplotly(ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = D, color = "Deceased")) +
  geom_point(shape = 20,data = datazariV, aes(x = as.Date(datumZ), y = minusD), color = "red") +
  theme_minimal() +
  ylab("Number of people") +
  labs(title = "Model comparison to real data ('Deceased')",color = "Legend"))

```

### Hospitalized

```{r}
ggplotly(ggplot(data, aes(x = datumy))  +
  geom_line(aes(y = H, color = "Hospitalized")) +
  geom_point(shape = 19,data = zaklad.stat, aes(x = as.Date(datum), y = aktualne_hospitalizovani), color = "red") +
  geom_hline(yintercept = kapacita, aes(color = "kapacita"), linetype="dashed", color = "black") +
  theme_minimal() +
  ylab("Number of people") +
  labs(title = "Model comparison to real data ('Hospitalized')",color = "Legend"))
```


Tests
=====================

Column 
---------------------
### Cumulative number of tests
```{r}
ggplotly(ggplot(testy, aes(as.Date(datum),kumulativni_pocet_testu)) +
  geom_line() +
  xlab("Date") +
  ylab("Number of tests") +
  labs(title = "Cumulative number of tests") + 
  theme_minimal())
```

Column 
---------------------

### Daily number of tests

```{r}
ggplotly(ggplot(testy, aes(as.Date(datum),prirustkovy_pocet_testu)) +
  geom_line() +
  xlab("Date") +
  ylab("Number of tests") +
  labs(title = "Daily number of tests") + 
  theme_minimal())

```

Column 
---------------------

### Rollmean of daily tests

```{r}
ggplotly(ggplot(testy.roll, aes(as.Date(Roll.Mean.Dates),Roll.Mean.Values)) +
  geom_line() +
  xlab("Date") +
  ylab("Rollmean of daily tests") +
  labs(title = title.plot) + 
  theme_minimal())
```

Column 
---------------------

### Rollmean of daily tests

```{r}
ggplotly(ggplot(testy.roll.Last.l, aes(as.Date(Roll.Mean.Dates.last.l),Roll.Mean.Values.last.l)) +
  geom_line() +
  xlab("Datum") +
  ylab("Rollmean of daily tests") +
  labs(title = title.plot.l, subtitle = title.plot) + 
  theme_minimal())
```

Cases
=====================
Column 
---------------------

### Cumulative number of infected

```{r}
ggplotly(ggplot(nakaza, aes(as.Date(datum),kumulativni_pocet_nakazenych)) +
  geom_line() +
  xlab("Date") +
  ylab("Cumulative number of infected") + 
  theme_minimal() + 
  labs(title = "Since the beginning"))
```

Column 
---------------------

### Daily number of infected

```{r}
ggplotly(ggplot(nakaza, aes(as.Date(datum),prirustkovy_pocet_nakazenych)) +
  geom_line() +
  xlab("Date") +
  ylab("Daily number of infected") + 
  theme_minimal() + 
  labs(title = "Since the beginning"))
```


Column 
---------------------

### Rollmean of new daily cases

```{r}
ggplotly(ggplot(nakaza.roll, aes(as.Date(Roll.Mean.Dates.nakaza),Roll.Mean.Values.nakaza)) +
  geom_line() +
  xlab("Date") +
  ylab("Rollmean of new daily cases") +
  labs(title = nakaza.title.plot) + 
  theme_minimal())
```

Column 
---------------------

### Rollmean of new daily cases

```{r}
ggplotly(ggplot(nakaza.roll.Last.l, aes(as.Date(Roll.Mean.Dates.last.l.nakaza),Roll.Mean.Values.last.l.nakaza)) +
  geom_line() +
  xlab("Date") +
  ylab("Rollmean of new daily cases") +
  labs(title = nakaza.title.plot.l, subtitle = nakaza.title.plot) + 
  theme_minimal())
```

Test positivity
=====================

Column 
---------------------
### Proportion of positive tests on all test
```{r}
ggplotly(ggplot(df.procenta, aes(as.Date(datum),procenta)) +
  geom_line() +
  xlab("Date") +
  ylab("Proportion of positive tests on all test") + 
  theme_minimal() + 
  labs(title = "Since the beginning"))
```

Column 
---------------------
### Chart A

```{r}

valueBox(paste(cpt,"%"), caption = "Test positivity since the beginning", icon = "ion-trophy")

```

### Chart B

```{r}

valueBox(paste(cpt30,"%"), caption = "Test positivity for the last 30 days", icon = "ion-trophy")

```

Column 
---------------------
### Per cent of positive tests
```{r}
ggplotly(ggplot(Last.l, aes(as.Date(Dates.last.l.procenta),Values.last.l.procenta)) +
  geom_line() +
  xlab("Date") +
  ylab("Per cent of positive tests") + 
  labs(title = procenta.title.plot.l) +
  theme_minimal())
```


Column 
---------------------
### Rollmean of positive tests
```{r}
ggplotly(ggplot(procenta.roll, aes(as.Date(Roll.Mean.Dates.procenta),Roll.Mean.Values.procenta)) +
  geom_line() +
  xlab("Date") +
  ylab("Rollmean of positive tests") +
  labs(title = procenta.title.plot) + 
  theme_minimal())
```


Column 
---------------------
### Rollmean of positive tests
```{r}
ggplotly(
ggplot(procenta.roll.Last.l, aes(as.Date(Roll.Mean.Dates.last.l.procenta),Roll.Mean.Values.last.l.procenta)) +
  geom_line() +
  xlab("Date") +
  ylab("Rollmean of positive tests") +
  labs(title = procenta.title.plot.l, subtitle = procenta.title.plot) + 
  theme_minimal())
```



Linear model
=====================

Column 
---------------------

### Since the beginning (new cases)

```{r}


testy <- read.csv(url.testy)
nakaza <- read.csv(url.nakaza)

jk <- ifelse(nrow(nakaza) == nrow(testy),procenta <-  nakaza$prirustkovy_pocet_nakazenych/testy$prirustkovy_pocet_testu, procenta <- nakaza$prirustkovy_pocet_nakazenych[1:(nrow(nakaza)-1)]/testy$prirustkovy_pocet_testu)


datum <- testy$datum
df.procenta <- data_frame(datum,procenta)
for.days <- 5

pripady <- nakaza$prirustkovy_pocet_nakazenych

f <- 1
for (f in 1:for.days) {
  
  pripady[length(pripady)+1] <- NA
  
}

min.date <- as.Date(nakaza$datum[1])
max.date <- as.Date(nakaza$datum[nrow(nakaza)]) + for.days
datum <- seq.Date(min.date,max.date,1)

temp <- 1:length(datum)

model <- data.frame(datum, temp, pripady)
nc <- ncol(model)

n <- 1
for (n in 1:for.days) {
  
  model <- cbind(model, NA)
  lin.model <- lm(model$pripady[1:(nrow(model)-7*n+7)] ~ model$temp[1:(nrow(model)-7*n+7)])
  pre.values <- lin.model$coefficients[1]+lin.model$coefficients[2]*model$temp
  model[1:(nrow(model)),nc+n] <- pre.values
  colnames(model)[nc+n] <- paste(n,".odhad")
  
}


odhady7.begin <- tail(model,1)

ggplotly(
  ggplot(data = model, aes(x = datum)) +
  geom_line(aes(y = `1 .odhad`, color = "1. estimate (today)")) +
  geom_line(aes(y = `2 .odhad`, color = "2. estimate (-7 days)")) +
  geom_line(aes(y = `3 .odhad`, color = "3. estimate (-14 days)")) +
  geom_line(aes(y = `4 .odhad`, color = "4. estimate (-21 days)")) +
  geom_line(aes(y = `5 .odhad`, color = "5. estimate (-28 days)")) +
  geom_line(aes(y = pripady, color = "Number of cases")) +
  theme_minimal() +
  labs(title = "Comparison of estimates") + 
  ylab("Number of cases")
    )


```



Column 
---------------------

### Last 60 days (new cases)

```{r}


n <- 1
model.range <- 60
model <- data.frame(datum, temp, pripady)
model60 <- tail(model, model.range)
nc <- ncol(model60)
title.model.range <- paste("In last ", model.range, "days")

for (n in 1:for.days) {
  
  model60 <- cbind(model60, NA)
  lin.model60 <- lm(model60$pripady[1:(nrow(model60)-7*n+7)] ~ model60$temp[1:(nrow(model60)-7*n+7)])
  pre.values <- lin.model60$coefficients[1]+lin.model60$coefficients[2]*model60$temp
  model60[1:(nrow(model60)),nc+n] <- pre.values
  colnames(model60)[nc+n] <- paste(n,".odhad")
  
}

ggplotly(
  ggplot(model60, aes(x = datum)) +
  geom_line(aes(y = `1 .odhad`, color = "1. estimate (today)")) +
  geom_line(aes(y = `2 .odhad`, color = "2. estimate (-7 days)")) +
  geom_line(aes(y = `3 .odhad`, color = "3. estimate (-14 days)")) +
  geom_line(aes(y = `4 .odhad`, color = "4. estimate (-21 days)")) +
  geom_line(aes(y = `5 .odhad`, color = "5. estimate (-28 days)")) +
  geom_line(aes(y = pripady, color = "Number of cases")) +
  theme_minimal() + 
  labs(title = "Comparison of estimates", subtitle = title.model.range) + 
  ylab("Number of cases")
)

odhady7.30 <- tail(model60,1)


```

Quadratic model
=====================

Column
---------------

### Since the beginning (new cases)

``` {r}

model <- data.frame(datum, temp, pripady)
nc <- ncol(model)

n <- 1
for (n in 1:for.days) {
  
  model <- cbind(model, NA)
  cas <- model$temp[1:(nrow(model)-7*n+7)]
  cas2 <- cas^2
  quad.model <- lm(model$pripady[1:(nrow(model)-7*n+7)] ~ cas + cas2)
  pre.values <- quad.model$coefficients[1] + quad.model$coefficients[2]*model$temp + quad.model$coefficients[3]*model$temp^2
  model[1:(nrow(model)),nc+n] <- pre.values
  colnames(model)[nc+n] <- paste(n,".odhad")
  
}

ggplotly(
ggplot(model, aes(x = datum)) +
  geom_line(aes(y = `1 .odhad`, color = "1. estimate (today)")) +
  geom_line(aes(y = `2 .odhad`, color = "2. estimate (-7 days)")) +
  geom_line(aes(y = `3 .odhad`, color = "3. estimate (-14 days)")) +
  geom_line(aes(y = `4 .odhad`, color = "4. estimate (-21 days)")) +
  geom_line(aes(y = `5 .odhad`, color = "5. estimate (-28 days)")) +
  geom_line(aes(y = pripady, color = "Number of cases")) +
  theme_minimal() +
  labs(title = "Comparison of estimates") + 
  ylab("Number of cases")
)

```

Column
---------------------

### Last 60 days (new cases)

```{r}

n <- 1
model.range <- 60
model <- data.frame(datum, temp, pripady)
model60 <- tail(model, model.range)
nc <- ncol(model60)
title.model.range <- paste("In last ", model.range, "days")

for (n in 1:for.days) {
  
  model60 <- cbind(model60, NA)
  cas <- model60$temp[1:(nrow(model60)-7*n+7)]
  cas2 <- cas^2
  quad.model60 <- lm(model60$pripady[1:(nrow(model60)-7*n+7)] ~ cas + cas2)
  pre.values <- quad.model60$coefficients[1] + quad.model60$coefficients[2]*model60$temp + quad.model60$coefficients[3]*model60$temp^2
  model60[1:(nrow(model60)),nc+n] <- pre.values
  colnames(model60)[nc+n] <- paste(n,".odhad")
  
}
ggplotly(
ggplot(model60, aes(x = datum)) +
  geom_line(aes(y = `1 .odhad`, color = "1. estimate (today)")) +
  geom_line(aes(y = `2 .odhad`, color = "2. estimate (-7 days)")) +
  geom_line(aes(y = `3 .odhad`, color = "3. estimate (-14 days)")) +
  geom_line(aes(y = `4 .odhad`, color = "4. estimate (-21 days)")) +
  geom_line(aes(y = `5 .odhad`, color = "5. estimate (-28 days)")) +
  geom_line(aes(y = pripady, color = "Number of cases")) +
  theme_minimal() +
  labs(title = "Comparison of estimates", subtitle = title.model.range) + 
  ylab("Number of cases")
)


```

Exponential model
=====================

Column
---------------------

### Last 60 days (new cases)

```{r}


datum <- testy$datum
for.days <- 5

pripady <- nakaza$prirustkovy_pocet_nakazenych

f <- 1
for (f in 1:for.days) {
  
  pripady[length(pripady)+1] <- NA
  
}

min.date <- as.Date(nakaza$datum[1])
max.date <- as.Date(nakaza$datum[nrow(nakaza)]) + for.days
datum <- seq.Date(min.date,max.date,1)



temp <- 1:length(datum)

model <- data.frame(datum, temp, pripady)
nc <- ncol(model)


n <- 1
model.range <- 60
model <- data.frame(datum, temp, pripady)
model60 <- tail(model, model.range)
nc <- ncol(model60)
title.model.range <- paste("In last ", model.range, "days")

for (n in 1:for.days) {
  
  model60 <- cbind(model60, NA)
  cas <- model60$temp[1:(nrow(model60)-7*n+7)]
  exp.model60 <- lm(log(model60$pripady[1:(nrow(model60)-7*n+7)]) ~ cas)
  pre.values <- exp(exp.model60$coefficients[1] + exp.model60$coefficients[2]*model60$temp)
  model60[1:(nrow(model60)),nc+n] <- pre.values
  colnames(model60)[nc+n] <- paste(n,".odhad")
  
}

ggplotly(
ggplot(model60, aes(x = datum)) +
  geom_line(aes(y = `1 .odhad`, color = "1. estimate (today)")) +
  geom_line(aes(y = `2 .odhad`, color = "2. estimate (-7 days)")) +
  geom_line(aes(y = `3 .odhad`, color = "3. estimate (-14 days)")) +
  geom_line(aes(y = `4 .odhad`, color = "4. estimate (-21 days)")) +
  geom_line(aes(y = `5 .odhad`, color = "5. estimate (-28 days)")) +
  geom_line(aes(y = pripady, color = "Number of cases")) +
  theme_minimal() +
  labs(title = "Comparison of estimates", subtitle = title.model.range) + 
  ylab("Number of cases")
)

exp.odhady7.30 <- tail(model60,1)
exp.odhady7.tom <- model60[nrow(model60)-4,1:(n+3)]


```